D_exp_2

### 2018-08-18 experiments/D_exp_2/writeup/D_exp_2.Rmd
recompiled D-exp-2

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

>>>>

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```
